Survivable Set Connectivity

### 2015-05-13 draft.tex
Started making changes to last section

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}

@@

\begin{lemma}[\cite{ssc}]
\label{lem:connected}
With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
\end{lemma}

\textbf{Proof Idea of Lemma~\ref{lem:connected}}:
\begin{enumerate}
\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$. Each flow path must go up the tree to some common ancestor $v$ and then back down.
\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
\end{enumerate}

@@

It remains to show that the probability that we find a path from $S_i$ to $T_i$ without using the edges from $F$ is at least $\beta$. We do this in the following lemma.
\end{proof}

@@

This concludes steps $3$ and $4$ of the proof idea for Lemma~\ref{lem:connectivity}. This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$. 
%
%\section{Potential Improvements}
%
%There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse. In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree. If there are multiple flow paths from different groups, say $(S_1', T_1')$ and $(S_2', T_2')$ going through $v$, then the original algorithm could find both at once. We could be finding $h$ paths with $O(\log n)$ cost (since running RoundGKR on each subtree makes each edge appear in $O(\log n)$ subtrees). 
%
%If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small). We can run the algorithm without looking for the nodes where the flow paths turn. In particular, we could treat it as many different instances of the Group Steiner Tree problem. The algorithm would be:
%\begin{codebox}
%\li Set $H \leftarrow \emptyset$
%\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
%\li Let $x' \leftarrow x*\frac{4}{k}$. 
%\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
%\li \For $\tau$ rounds \Do
%\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
%\li \For $q = 0, ..., 2\log n$ \Do
%\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
%\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
%\li \If $s$ is $q$-marked \Then
%\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
%\li \For $\tau'$ iterations, \Do
%\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
%\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
%\li return $H$
%\end{codebox}
%The main difference lies in line 8. Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins. We know all flow paths go from $S_i'$ to $T_i'$, so we make $s \in S_i'$ the root of the tree. It is unnecessary to look for where the flow turns. We still have to iterate through $q= 0, ..., 2\log n$, since the flow of at least $1$ between $S_i'$ and $T_i'$ might be divided among different flow paths starting at different nodes in $S_i'$. This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
%
%Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
%
%\begin{lemma}
%The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
%\end{lemma}
%
%\begin{proof}
%The proof is the same as the proof of Lemma~\ref{lem:cost}. The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps. 
%\end{proof}
%
%Therefore, if $S = o(\log n)$, it is better to run this modified algorithm. Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want. If $T = O(\log n)$, then the tree could be compressed to size $O(\log n)$, and so we would find unit flow paths with probability $\Omega(\frac{1}{\log \log n})$. This means we could reduce $\tau'$ to $O(\log \log n)$ and decrease our approximation ratio.
%
%Now the question becomes, can we reduce $S$ to $h$? One possible idea is to join all the nodes in $S_i'$. This would destroy the tree property for RoundGKR, but maybe we can disregard some cycles (at least if we analyzed the case with unit costs on the edges). \cite{ssc} uses RoundGKR and R\"{a}cke trees as black boxes, so maybe there is some hope. If this is possible, then our competitiveness would be $O(h\log^3n(\dfrac{\log h}{k} + 1))$. Now if $h = o(\log n)$, then we would prefer this algorithm.

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}

@@

Now, we can state the theorem we need for the desired connectivity claim. Note that since $\alpha = O(\log n)$, the following result says that between each $S_i$ and $T_i$, we have $\Omega(\frac{k}{\log n})$ paths.

\begin{theorem}[\cite{ssc}]
\label{theorem:connected}
With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
\end{theorem}

As the proof of this theorem is complicated, we break up the overall structure of the theorem into five parts.

\textbf{Proof Structure for Theorem~\ref{theorem:connected}}:
\begin{enumerate}
\item Select a particular set of edges $F \subseteq E$ of size at most $\Omega(\dfrac{k}{\log n})$. 
\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
\item Condition on this probability to show that if we remove $\text{map}(F)$ from the tree, we still have sufficient flow from each $S_i$ to $T_i$. Each flow path must go up the tree to some common ancestor $v$ and then back down.
\item Then we will claim that some $v$ gets $q$-marked for some $q$ and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $S_i$ and $T_i$, and so the path will be included with sufficient probability and exclude $F$.
\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
\end{enumerate}

@@

It remains to show that the probability that we find a path from $S_i$ to $T_i$ without using the edges from $F$ is at least $\beta$. We do this in the following lemma.

@@

This concludes steps $3$ and $4$ of the proof idea for Lemma~\ref{lem:connectivity}. This finishes the proof that after running the rounding algorithm, each $(S_i, T_i)$ tuple will have $\Omega(\frac{k}{\log n})$ paths connecting $S_i$ to $T_i$.

\end{proof}

%
%\section{Potential Improvements}
%
%There seems to be a trade off in the algorithm between finding flow paths between many groups at once and searching for nodes the flow paths traverse. In the original algorithm, we must iterate through each $v \in V_T$ and run some RoundGKRrounds on its subtree. If there are multiple flow paths from different groups, say $(S_1', T_1')$ and $(S_2', T_2')$ going through $v$, then the original algorithm could find both at once. We could be finding $h$ paths with $O(\log n)$ cost (since running RoundGKR on each subtree makes each edge appear in $O(\log n)$ subtrees). 
%
%If we know $\sum_{i=1}^h |S_i| = S$ is small (the number of sources is small). We can run the algorithm without looking for the nodes where the flow paths turn. In particular, we could treat it as many different instances of the Group Steiner Tree problem. The algorithm would be:
%\begin{codebox}
%\li Set $H \leftarrow \emptyset$
%\li Compute linear program SSC-LP and set to zero any $x_e < \dfrac{k}{n^2}$.
%\li Let $x' \leftarrow x*\frac{4}{k}$. 
%\li Let $\mathcal{D}$ be the distribution of R\"{a}cke's tree embeddings for $G$ with $x'$.
%\li \For $\tau$ rounds \Do
%\li Sample $(T, y, \text{map})$ from $\mathcal{D}$. 
%\li \For $q = 0, ..., 2\log n$ \Do
%\li \For \For $i \in [h]$ and $s \in S_i'$ \Do
%\li With probability $\min\{1, \dfrac{4}{2^q}\}$, $q$-mark $s$
%\li \If $s$ is $q$-marked \Then
%\li Set $y^{s, q}\leftarrow 2^{q+1}y$ and $E^{s,q} \leftarrow \emptyset$.
%\li \For $\tau'$ iterations, \Do
%\li $E^{s,q} \leftarrow E^{s,q} \cup$ RoundGKR$(T_s, s, y^{s,q})$ \End
%\li $H \leftarrow H \cup \text{map}(E^{s,q})$ \End \End \End \End
%\li return $H$
%\end{codebox}
%The main difference lies in line 8. Instead of iterating through all $v \in V_T$ to find where the flow path turns, we take advantage of knowing where the flow begins. We know all flow paths go from $S_i'$ to $T_i'$, so we make $s \in S_i'$ the root of the tree. It is unnecessary to look for where the flow turns. We still have to iterate through $q= 0, ..., 2\log n$, since the flow of at least $1$ between $S_i'$ and $T_i'$ might be divided among different flow paths starting at different nodes in $S_i'$. This gets rid of the $O(\log n)$ factor in the cost because of the height, and adds a factor of $S$.
%
%Lemma~\ref{lem:connected} still holds. Since we know exactly where the flow paths must start.
%
%\begin{lemma}
%The above algorithm has $\textbf{E}[c(H)] = O(S\log^3 n(\dfrac{\log h}{k} + 1))*c(x)$.
%\end{lemma}
%
%\begin{proof}
%The proof is the same as the proof of Lemma~\ref{lem:cost}. The only difference is that instead of each edge being included in at most $height(T)$ RoundGKR steps, we include it in at most $S$ RoundGKR steps. 
%\end{proof}
%
%Therefore, if $S = o(\log n)$, it is better to run this modified algorithm. Along similar lines, if $\sum_{i \in [h]} |T_i| = T$ is small, then we could compress the R\"{a}cke tree to contain only the leaves we want. If $T = O(\log n)$, then the tree could be compressed to size $O(\log n)$, and so we would find unit flow paths with probability $\Omega(\frac{1}{\log \log n})$. This means we could reduce $\tau'$ to $O(\log \log n)$ and decrease our approximation ratio.
%
%Now the question becomes, can we reduce $S$ to $h$? One possible idea is to join all the nodes in $S_i'$. This would destroy the tree property for RoundGKR, but maybe we can disregard some cycles (at least if we analyzed the case with unit costs on the edges). \cite{ssc} uses RoundGKR and R\"{a}cke trees as black boxes, so maybe there is some hope. If this is possible, then our competitiveness would be $O(h\log^3n(\dfrac{\log h}{k} + 1))$. Now if $h = o(\log n)$, then we would prefer this algorithm.
